Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-17 doc/manuscript/ESSDmanuscript.Rmd
add table of ForC changes

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Schematic illustrating the carbon pools quantified under IPCC accounting; ForC variables corresponding to the stock, increment, influx and outflux; and relationships among them. In many cases, the match of ForC variables to IPCC criteria depends upon measurement protocols (e.g., minimum DBH). Additional caveats are as follows: 1- assumes minimal non-respiratory CO2 fluxes,... (Chapin et al. 2006); 2- assumes that change in foliage biomass is negligible (see note 7); 3- incomplete: excludes large branch fall; also, under IPCC definitions, outflux from aboveground biomass should include all sizes, influx to deadwood should include only above the minimum diameter chosen for dead wood; 4- incomplete: excludes belowground components;  5-incomplete: excludes breakage into pieces less than dead wood threshold size; 6-incomplete: excludes woody mortality of stems <10 cm DBH, decomposition of dead wood (aboveground and coarse roots) into sizes classified as litter; 7-foliage production is generally measured by collecting leaf-fall, a method that assumes that the influx = outflux (foliage biomass is roughly constant year-to-year)."}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/C_variable_mapping.png")
```

@@

Define relationship among NEE, NEP, and delta.C., especially noting role of harvest.

@@

```{r, out.width = "12cm", echo = FALSE,fig.pos="H", fig.cap = "Table of changes to ForC fields (placeholder) "}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/ForC_updates_placeholder_fig.png")
```
*(The above is a placeholder for the table located at  https://github.com/forc-db/ForC/blob/master/database_management_records/record_of_changes.csv, which we'll need to format.)*

>>>>

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Schematic illustrating the carbon pools quantified under IPCC accounting; ForC variables corresponding to the stock, increment, influx and outflux; and relationships among them. In many cases, the match of ForC variables to IPCC criteria depends upon measurement protocols (e.g., minimum DBH). Additional caveats are as follows: 1- assumes minimal non-respiratory C fluxes,... (Chapin et al. 2006); 2- assumes that change in foliage biomass is negligible (see note 7); 3- incomplete: excludes large branch fall; also, under IPCC definitions, outflux from aboveground biomass should include all sizes, influx to deadwood should include only above the minimum diameter chosen for dead wood; 4- incomplete: excludes belowground components;  5-incomplete: excludes breakage into pieces less than dead wood threshold size; 6-incomplete: excludes woody mortality of stems <10 cm DBH, decomposition of dead wood (aboveground and coarse roots) into sizes classified as litter; 7-foliage production is generally measured by collecting leaf-fall, a method that assumes that the influx = outflux (foliage biomass is roughly constant year-to-year)."}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/C_variable_mapping.png")
```

@@

Define relationship among NEE, NEP, and delta.C., especially noting role of harvest [@chapin_reconciling_2006].

@@

```{r table_ForCchanges, eval = TRUE, echo=FALSE, warning=FALSE}
#"figures_tables/record_of_changes.csv" is copied over from the table located at  https://github.com/forc-db/ForC/blob/master/database_management_records/record_of_changes.csv, and I deleted the date field.

record_of_changes <- read.csv("figures_tables/record_of_changes.csv")
names(record_of_changes) <- stringr::str_replace_all(names(record_of_changes), "\\.", " ")

library(knitr)
library(kableExtra)
knitr::kable(record_of_changes, format = "latex",
             longtable = FALSE,
             caption = "\\textbf{Table of changes to ForC fields.}") %>%
  kableExtra::kable_styling(full_width = TRUE) %>%
  row_spec(0, bold = TRUE)
```

### 2021-06-17 doc/manuscript/ESSDmanuscript.tex
add table of ForC changes

\begin{figure}
\includegraphics[width=12cm]{figures_tables/C_variable_mapping} \caption{Schematic illustrating the carbon pools quantified under IPCC accounting; ForC variables corresponding to the stock, increment, influx and outflux; and relationships among them. In many cases, the match of ForC variables to IPCC criteria depends upon measurement protocols (e.g., minimum DBH). Additional caveats are as follows: 1- assumes minimal non-respiratory CO2 fluxes,... (Chapin et al. 2006); 2- assumes that change in foliage biomass is negligible (see note 7); 3- incomplete: excludes large branch fall; also, under IPCC definitions, outflux from aboveground biomass should include all sizes, influx to deadwood should include only above the minimum diameter chosen for dead wood; 4- incomplete: excludes belowground components;  5-incomplete: excludes breakage into pieces less than dead wood threshold size; 6-incomplete: excludes woody mortality of stems <10 cm DBH, decomposition of dead wood (aboveground and coarse roots) into sizes classified as litter; 7-foliage production is generally measured by collecting leaf-fall, a method that assumes that the influx = outflux (foliage biomass is roughly constant year-to-year).}\label{fig:unnamed-chunk-1}
\end{figure}

@@

Define relationship among NEE, NEP, and delta.C., especially noting role
of harvest.

@@

\begin{figure}[H]
\includegraphics[width=12cm]{figures_tables/ForC_updates_placeholder_fig} \caption{Table of changes to ForC fields (placeholder) }\label{fig:unnamed-chunk-2}
\end{figure}

\emph{(The above is a placeholder for the table located at
https://github.com/forc-db/ForC/blob/master/database\_management\_records/record\_of\_changes.csv,
which we'll need to format.)}

>>>>

\begin{figure}
\includegraphics[width=12cm]{figures_tables/C_variable_mapping} \caption{Schematic illustrating the carbon pools quantified under IPCC accounting; ForC variables corresponding to the stock, increment, influx and outflux; and relationships among them. In many cases, the match of ForC variables to IPCC criteria depends upon measurement protocols (e.g., minimum DBH). Additional caveats are as follows: 1- assumes minimal non-respiratory C fluxes,... (Chapin et al. 2006); 2- assumes that change in foliage biomass is negligible (see note 7); 3- incomplete: excludes large branch fall; also, under IPCC definitions, outflux from aboveground biomass should include all sizes, influx to deadwood should include only above the minimum diameter chosen for dead wood; 4- incomplete: excludes belowground components;  5-incomplete: excludes breakage into pieces less than dead wood threshold size; 6-incomplete: excludes woody mortality of stems <10 cm DBH, decomposition of dead wood (aboveground and coarse roots) into sizes classified as litter; 7-foliage production is generally measured by collecting leaf-fall, a method that assumes that the influx = outflux (foliage biomass is roughly constant year-to-year).}\label{fig:unnamed-chunk-1}
\end{figure}

@@

Define relationship among NEE, NEP, and delta.C., especially noting role
of harvest \citep{chapin_reconciling_2006}.

@@

\caption{\label{tab:table_ForCchanges}\textbf{Table of changes to ForC fields.}}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
\textbf{Table} & \textbf{Column} & \textbf{Description} & \textbf{Changes} & \textbf{Motivation}\\
\hline
Sites & coordinates.precision & Precision of geographic coordinates, as reported by source or estimated from maps. & field added & allow identification of records with poor coordinate precision\\
\hline
Measuremennts & data.location.within.source & Location of data within the source listed in citation.ID. & field added & facilitate review, ensure traceability\\
\hline
 & sd, se, lower95\%CI, upper 95\%CI & Standard deviation, standard error, and lower and upper 95 percent confidence intvervals, respectively. & replaces `stat` and `stat.name` & cleaner format; ability to handle assymetrical 95 percent confidence intervals\\
\hline
 & mean.in.original.units, original.units & mean value and units presented in original publication & fields added & provide IPCC with original units, reduce errors/improve reproducibility\\
\hline
 & C.conversion.factor & Assumed/ measured C content of organic matter used to convert organic matter to C. & field added & track units conversion, allow back-calculation of OM if conversion factor deemed inappropriate\\
\hline
PFT & description & Definition of the pftcode at the community level. Differs from individual level in that properly describes mixed plant functional types. & field added & \\
\hline
 & description.individual & Definition of the pftcode at the individual plant level. & field name change (previously `description`) & \\
\hline
Citations & (several fields) &  &  & \\
\hline
\end{tabu}
\end{table}
